Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex
finished def of centralizer qua fact alg

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh))
\]
equipped with a convolution-type product.
\end{thm}

@@

\begin{lmm}
\label{lmm: CE from map}
\owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
\end{lmm}

@@

Our goal here is to construct the factorization algebra that models the centralizer.
First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra.

The role of

The lemma allows us to define the factorization algebra given on any open $U$ by  the Chevalley-Eilenberg chain complexes
$ \cliels\big(\fg \otimes \Omega^*_c(U), \bU_n \fh(U) \big)$ (with their standard differential)
of $\fg \otimes \Omega^*_c(U)$ with value on $\bU_n \fh(U)$ whose structure maps are given, for any $(U_i)_{i\in I}$ 
a finite family of pairwise disjoint open subsets of an open $V$, by 
\begin{multline}\label{eq:transClieFac}
 \bigotimes_{i\in I} \cliels\big(\fg \otimes \Omega^*_c(U_i), \bU_n \fh(U_i) \big) \cong Sym\Big(
 \fg\otimes (\bigoplus_{i\in I}  \Omega^*_c(U_i))[-1]  \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big) \\ 
 \cong Sym\Big(\fg\otimes \Omega_c\big(\coprod U_i\big)[-1] \Big) \otimes \Big( \bigotimes_{i\in I} B(U_i)\Big)  
 \stackrel{\omega^*\otimes \mu_B}\longrightarrow Sym(\fg\otimes \Omega_c(V)[-1] ) \otimes B(V) \\ 
 = \cliels(\fg\otimes \Omega_c(V), B(V))
\end{multline}
where $\omega$ is induced by the cosheaf structure of compactly supported form and $\mu_B$ is the factorization algebra structure of $B$.

The (homotopy) sheaf structure of forms also gives us structure maps
\begin{multline}\label{eq:transClieFacCochain}
 \bigotimes_{i\in I} \clies\big(\fg \otimes \Omega^*(U_i), B(U_i) \big) \longrightarrow
  \Hom\Big(Sym\big(\fg\otimes (\bigoplus_{i\in I}  \Omega^*(U_i))[-1]\big),  \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \cong \Hom\Big(Sym\big(\fg\otimes \Omega^*(\coprod U_i)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\rho}\longrightarrow \Hom\Big(Sym\big(\fg\otimes \Omega^*(V)[-1]\big), \bigotimes\limits_{i\in I} B(U_i) \Big) \\
 \stackrel{\mu_B}\longrightarrow 
  \clies(\fg\otimes \Omega (V), B(V))
\end{multline}
where $\rho$ is given by the restriction of forms onto a subspace.

\label{L:ClieFacDef} 
 Similarly, the structure maps~\eqref{eq:transClieFacCochain} makes 
 $ \clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ a (resp. locally constant) factorization algebra.

\begin{dfn}\label{dfn:CEofFact}
We {call   $\cliels\big(\fg \otimes \Omega^*_c, \bU_n \fh \big)$ the Chevalley-Eilenberg chain factorization algebra of $\fg$ with value in $\bU_n \fh$} 
and $\clies\big(\fg \otimes \Omega^*, \bU_n \fh \big)$ the Chevalley-Eilenberg cochain factorization algebra.
\end{dfn}
\begin{proof}

A special but very interesting case is of course when $\bU_n \fh$ is itself an enveloping algebra. 
\begin{cor}
 Let $\fg$, $\fh$ be dg-Lie algebras and $f:\fg\to \fh$ be a dg-Lie algebra morphism. 
 Then the induced factorization algebra map $\mathbf{\UU_n f}:  \cliels( \fg \otimes \Omega^*_c) \longrightarrow  \cliels( \fh \otimes \Omega^*_c) $
 is the standard map $\cliels(f)$ induced by $f$ and the action of $\fg  \otimes \Omega^*_c$ is obtained from the $\fg$-action on $\fh$ by Leibniz rule.
\end{cor}
\begin{rmk}\greg{Extends to $L_\infty$ case in a sentence or too}
\end{rmk}

\owen{Add a remark on convolution}
%
%\def\conv{{\rm Conv}}
%
%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
%
%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}
%
%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}

>>>>

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer ${\frak Z}_{E_n}(f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

\begin{dfn}
\label{dfn: CE from map}
\owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
\end{dfn}

@@

Our goal here is to construct the factorization algebra that models the centralizer.
First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra and to verify it forms a factorization algebra.

\begin{rmk}
These arguments are now standard in the literature of factorization algebras, so we will be brief in our discussion.
See, e.g., \cite{CG1} \owen{stuff by Greg and others} for more.
\end{rmk}

Consider now a fixed open set $V \subset \RR^n$.
Then the $L_\infty$ map $f: \fg \rightsquigarrow \fh$ induces canonically an $L_\infty$ map 
\[
\tilde{f}: \Omega^*_c(V) \otimes \fg \to \Omega^*_c(V) \otimes \fh
\]
by base change along the map $k \to \Omega^*_c(V)$ of dg commutative algebras,
as the compactly supported de Rham forms form a dg commutative algebra under wedge product.
In consequence, we see that $\Omega^*_c(V) \otimes \fg$ acts on $\Omega^*_c(V) \otimes \fh$ and hence equips it with the structure of an $L_\infty$ module over $\Omega^*_c(V) \otimes \fg$.
We denote this module as
\[
(\Omega^*_c(V) \otimes \fh)_f
\]
to emphasize the dependence on the original map~$f$.
In this action, the wedge product of forms intertwines with the $L_\infty$ structure on $\fg$ in a very simple way: 
they simply happen side by side, but do not affect each other.

Observe that $\Omega^*_c(V)$ is a module over the dg commutative algebra $\Omega^*(V)$ of {\em non}\/compactly supported forms.
This action extends immediately to the module $(\Omega^*_c(V) \otimes \fh)_f$, so we now view it as an $L_\infty$ module over $\Omega^*(V)$ as well.
In consequence, we have a cochain complex
\[
\clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
\]
on each open set~$V$.

The next step is to verify functoriality of this construction over the poset of opens.
This property follows quickly from the fact that wedge product of forms preserves support.
Given an inclusion $i: V' \subset V$ of opens, if we take a form $\alpha \in \Omega^*(V)$ and a compactly supported form $\beta \in \Omega^*_c(V')$, then the wedge product $\alpha \wedge i_* \beta \in \Omega^*_c(V)$ after applying the extension-by-zero map $i_*: \Omega^*_c(V') \to \Omega^*_c(V)$ equals the wedge product $i_*(i^*\alpha \wedge \beta)$ arising from the restriction $i^* \alpha$ of $\alpha$ to~$V'$.
In consequence, the action of $\Omega^*(V) \otimes \fg$ on $(\Omega^*_c(V') \otimes \fh)_f$ arising from the restriction map $\Omega^*(V) \otimes \fg \to \Omega^*(V') \otimes \fg$ of $L_\infty$ algebras agrees with action induced by the inclusion of $(\Omega^*_c(V') \otimes \fh)_f$ as a (strict) submodule of~$(\Omega^*_c(V) \otimes \fh)_f$.
This argument is manifestly associative under composition of inclusions, so we have shown our first claim.

\begin{lmm}
The assignment
\[
V \mapsto \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
\]
determines a functor from ${\rm Opens}_{\RR^n}$ to~$\Ch_k$.
\end{lmm}

We now turn to extending this functor to an algebra over the colored operad ${\rm Opens}_{\RR^n}^\sqcup$ whose colors are opens in $\RR^n$ where there is a precisely a single operation from a tuple of opens $[V_1,\ldots,V_k]$ to an open $W$ if and only if both $W$ contains every $V_j$ and the $V_j$ are all pairwise disjoint.

The key fact is that the functors $\cliels$ and $\clies$ are suitably symmetric monoidal:
they send a product of $L_\infty$ algebras to a tensor product of cochain complexes.
Hence it suffices to examine the underlying functors to $L_\infty$ algebras.
As the functors $\Omega^*$ and $\Omega^*_c$ send finite disjoint unions of opens to the direct product of cochain complexes, 
the functors like $\Omega^* \otimes \fg$ and $\Omega^*_c \otimes \fh$ send finite disjoint unions of opens to products of $L_\infty$ algebras.
In consequence, we obtain the desired second claim.

\begin{lmm}
The assignment
\[
V \mapsto \clies(\Omega^*(V) \otimes \fg, (\Omega^*_c(V) \otimes \fh)_f)
\]
determines a prefactorization algebra, i.e., a strict algebra over ${\rm Opens}_{\RR^n}^\sqcup$ with values in~$\Ch_k^\otimes$.
\end{lmm}

Due to the Poincar\'e lemma, the inclusion of a disk into a bigger disk $D \hookrightarrow D'$ makes the structure map 
\[
\clies(\Omega^*(D) \otimes \fg, (\Omega^*_c(D) \otimes \fh)_f) \xto{\simeq} \clies(\Omega^*(D) \otimes \fg, (\Omega^*_c(D) \otimes \fh)_f)
\]
a quasi-isomorphism.
Hence this prefactorization algebra is locally constant in a homotopical sense.

In fact, it defines a {\em factorization} algebra, by arguments that can be found in \owen{chapter 6 of \cite{CG1} and elsewhere}.

\owen{Add a remark on convolution?}
%
%\def\conv{{\rm Conv}}
%
%\owen{For an ordinary colored operad $\cO$, describe how to produce a $\cO$-algebra $\conv(C,A)$ from any $\cO$-coalgebra $C$ and $\cO$-algebra $A$.}
%
%\owen{A special case to consider is how a cocycle $f \in \conv(C,A)$ encodes an $\cO$-algebra morphism $C^! \to A$ from $C^! = \conv(C,1)$, the ``Koszul dual'' $\cO$-algebra to the coalgebra $C$. This cocycle can be used to twist the differential of $\conv(C,A)$. Hopefully this admits an obvious deformation-theoretic interpretation.}
%
%\owen{If we do this correctly, we might find a model category-theoretic picture of how Koszul duality works for prefactorization algebras.}
